### 2023-02-09 article.tex
Improve

% \paragraph{The drawbacks of publishing code}

@@

% \paragraph{The drawbacks of publishing version-controlled code}

@@

% \paragraph{The drawbacks of publishing a running version of code}

@@

% \paragraph{Final word}

>>>>

\paragraph{The drawbacks of publishing code}

@@

\paragraph{The drawbacks of publishing version-controlled code}

@@

\paragraph{The drawbacks of publishing a running version of code}

@@

The simplest and most impactful step to make code more useful paradata
is, however, to publish it on a code hosting website 
along a publication. From then on, the next steps can be taken 
gradually as the skills of the author(s) progress.

\paragraph{Final word}
